%Summarize what was learned. 
%Summarize the results.
%Future Plans
%What I did wrong
%%Subsection: Improvements to ReG-Tries
%%Subsection: Reflection on St. Mary's Project
\subsection{The Current State of Network Motifs in Brain Networks}
The current paper revealed methodology for discovering and analyzing network motifs in large brain networks. The GTries algorithm performed adequately in network motif detection on 520 individuals across 6 thresholds - making it a viable algorithm for motif discovery in brain networks, especially given its reported running time. Suggestions were made to further improve the GTries algorithm specifically in the realm of brain networks research. Current algorithms in graph isomorphism seem to outperform those used in the GTries algorithm, however, successful implementation would be needed as proof. A novel methodology in studying network motifs in brain networks was used in the current study, which revealed a significant difference in the distribution of 4 order subgraphs in functional brain networks of individuals with ADHD versus those without. This provided a proof-of-concept for the methodology. 
\subsection{St. Mary's Project Reflection}
There are many things that I wish I had done early on during my St. Mary's Project experience that would have helped out in the long-run:
\begin{itemize}
\item{Narrowed down on a topic early}
\item{Toned down my ambition}
\item{Collaborated with my SMP advisor}
\item{Set deadlines for myself which I knew I wouldn't be able to keep}
\end{itemize}
As a result of these missteps, I ended up spending a dispropportionate amount of my time researching what I should do for my SMP. This occured until this semester, which very much made even later missteps I made hurt much worse. Were I to repeat my SMP, I would definitely \textit{not} let myself choose my own topic. Rather, I would have my advisor instruct me the entire way. Because I chose a topic that was not an area my SMP advisor had expertise, nor was it a topic which anyone at the school had expertise in, I took it upon myself to become my own advisor on the matter, which ended in me turning in my SMP late. Overall, I have a lot of regrets about how I handled myself on this project, and I wish that I had realized the self-defeating cycle I would be getting myself into - and stopped doing things according to my schedule. At this point in time though, I am just really really glad that I am finished. 